%% ----------------------------------------------------------------
%% Thesis.tex -- MAIN FILE (the one that you compile with LaTeX)
%% ---------------------------------------------------------------- 

% Set up the document
\documentclass[a4paper, 11pt, oneside]{Thesis}  % Use the "Thesis" style, based on the ECS Thesis style by Steve Gunn
\graphicspath{Images/}  % Location of the graphics files (set up for graphics to be in PDF format)

% Include any extra LaTeX packages required
\usepackage[square, numbers, comma, sort&compress]{natbib}  % Use the "Natbib" style for the references in the Bibliography
\usepackage{verbatim}  % Needed for the "comment" environment to make LaTeX comments
\usepackage{vector}  % Allows "\bvec{}" and "\buvec{}" for "blackboard" style bold vectors in maths
\hypersetup{urlcolor=blue, colorlinks=true}  % Colours hyperlinks in blue, but this can be distracting if there are many links.
\usepackage{float}
\usepackage{times}
\usepackage{graphicx} % more modern
\usepackage{subfigure}
%\usepackage{natbib}
\usepackage{amsmath}
\usepackage{enumerate}
%\usepackage{bbm}
\usepackage{makecell}
%\usepackage{booktabs}
\usepackage{tabularx}
\usepackage{multirow, bm, threeparttable}
\usepackage[usenames,dvipsnames,table]{xcolor}
\usepackage{csvsimple}
\usepackage{siunitx}
\usepackage{bbm}
\usepackage{bibentry}
%\usepackage{ulem}
%\usepackage{pdfpages}
%\usepackage{fullpage}
\usepackage{changes}
\newcolumntype{R}{>{$}r<{$}}
\newcolumntype{L}{>{$}l<{$}}
\newcolumntype{M}{R@{${}={}$}L}
\usepackage{multirow}


% math
\DeclareMathOperator*{\Mean}{Mean}
\DeclareMathOperator*{\Median}{Median}

% For algorithms
\usepackage{algorithm}
\usepackage{algorithmic}
\usepackage{hyperref}
\renewcommand{\thefigure}{A\arabic{figure}}
\renewcommand{\thetable}{A\arabic{table}}

\usepackage{pdflscape}
\usepackage{afterpage}
\usepackage{capt-of}
% other
\renewcommand\thesection{\Alph{section}}

%\newcommand{\theHalgorithm}{\arabic{algorithm}}

\newcommand{\tabincell}[2]{\begin{tabular}{@{}#1@{}}#2\end{tabular}}

\renewcommand{\thetable}{S\arabic{table}}
%% ----------------------------------------------------------------
\begin{document}
\frontmatter      % Begin Roman style (i, ii, iii, iv...) page numbering

% Set up the Title Page
\title  {Molecular Machine Learning with DeepChem}
\authors  {\texorpdfstring
            {\href{https://rbharath.github.io}{Bharath Ramsundar}}
            {Bharath Ramsundar}
            }
\addresses  {\groupname\\\deptname\\\univname}  % Do not change this here, instead these must be set in the "Thesis.cls" file, please look through it instead
\date       {\today}
%\subject    {}
%\keywords   {}

\maketitle
%% ----------------------------------------------------------------

\setstretch{1.3}  % It is better to have smaller font and larger line spacing than the other way round

% Define the page headers using the FancyHdr package and set up for one-sided printing
\fancyhead{}  % Clears all page headers and footers
\rhead{\thepage}  % Sets the right side header to show the page number
\lhead{}  % Clears the left side page header

\pagestyle{fancy}  % Finally, use the "fancy" page style to implement the FancyHdr headers

%% ----------------------------------------------------------------
% Declaration Page required for the Thesis, your institution may give you a different text to place here
\Declaration{

\addtocontents{toc}{\vspace{1em}}  % Add a gap in the Contents, for aesthetics

I, Bharath Ramsundar, declare that this thesis titled, `Molecular Machine Learning with DeepChem' and the work presented in it are my own. I confirm that:

\begin{itemize} 
\item[\tiny{$\blacksquare$}] This work was done wholly or mainly while in candidature for a research degree at this University.
 
\item[\tiny{$\blacksquare$}] Where any part of this thesis has previously been submitted for a degree or any other qualification at this University or any other institution, this has been clearly stated.
 
\item[\tiny{$\blacksquare$}] Where I have consulted the published work of others, this is always clearly attributed.
 
\item[\tiny{$\blacksquare$}] Where I have quoted from the work of others, the source is always given. With the exception of such quotations, this thesis is entirely my own work.
 
\item[\tiny{$\blacksquare$}] I have acknowledged all main sources of help.
 
\item[\tiny{$\blacksquare$}] Where the thesis is based on work done by myself jointly with others, I have made clear exactly what was done by others and what I have contributed myself.
\\
\end{itemize}
 
 
Signed:\\
\rule[1em]{25em}{0.5pt}  % This prints a line for the signature
 
Date:\\
\rule[1em]{25em}{0.5pt}  % This prints a line to write the date
}
\clearpage  % Declaration ended, now start a new page

%% ----------------------------------------------------------------
% The "Funny Quote Page"
%\pagestyle{empty}  % No headers or footers for the following %pages

%\null\vfill
%% Now comes the "Funny Quote", written in italics
%\textit{``Write a funny quote here.''}

%\begin{flushright}
%If the quote is taken from someone, their name goes here
%\end{flushright}

%\vfill\vfill\vfill\vfill\vfill\vfill\null
%\clearpage  % Funny Quote page ended, start a new page
%% ----------------------------------------------------------------

% The Abstract Page
\addtotoc{Abstract}  % Add the "Abstract" page entry to the Contents
\abstract{
\addtocontents{toc}{\vspace{1em}}  % Add a gap in the Contents, for aesthetics


Machine learning has widely been applied to image, video, and
speech datasets, but has not yet achieved broad penetration into
chemistry, materials science, or other molecular design applications. However, over the last few years, machine learning and deep learning have achieved notable successes in predicting properties of molecular systems. In this thesis, I present a series of deep learning algorithms that demonstrate strong predictive improvements across a wide range of biochemical tasks such as assay activity modeling, toxicity prediction, protein-ligand binding affinity calculation, and chemical retrosynthesis. In addition to these algorithmic improvements, I introduce the comprehensive benchmark suite MoleculeNet for molecular machine learning algorithms (https://moleculenet.ai) and demonstrate how the technology of one-shot learning can be used for drug discovery applications. The work presented in this thesis culminated in my design and construction of DeepChem (https://deepchem.io), an open source package for molecular machine learning, which has achieved broad adoption among biotech startups, pharmaceutical companies, and research groups. DeepChem has attracted a thriving community of open source developers and looks to continue growing and expanding as a vibrant research tool. 
}

\clearpage  % Abstract ended, start a new page
%% ----------------------------------------------------------------

\setstretch{1.3}  % Reset the line-spacing to 1.3 for body text (if it has changed)

% The Acknowledgements page, for thanking everyone
\acknowledgements{
\addtocontents{toc}{\vspace{1em}}  % Add a gap in the Contents, for aesthetics

My thanks to the computer science department at Stanford for taking a chance on a student who'd previously spent more time working on math than on computers.

My thanks to Robert McGibbon for my initial introduction to computational chemistry. To Steven Kearnes for teaching me about computational drug discovery. To David Konerding for letting me take on a crazy internship project at Google working on drug discovery. To Patrick Riley and the GAS team at Google for giving me the opportunity to continue exploring deep learning and drug discovery at Google. To Evan Feinberg for explaining and exploring protein binding with me. To Joe Gomes for teaching me some quantum chemistry and force field design. To Michael Wu for working with me on a small benchmarking project that grew into a multiyear effort. To Bowen Liu for helping me understand chemical synthesis. To Aneesh Pappu for being a great summer intern. To Prasad Kawthekar for exploring the DeepChem GUI and synthesis with me.

My thanks to my industrial collaborators from pharma, Denny Rajiah, Govindan Subramanian, Robert Sheridan, Andreas Verras, and Matthew Tudor for taking a chance on experimenting with untested machine learning methods.

I'd especially like to acknowledge the entire DeepChem development team. It's your efforts that have transformed a few scripts on GitHub into a thriving open source project and community. Special thanks to Peter Eastman, Karl Leswing, and Michael Wu for all the time they've put in. More generally, my heartfelt thanks to our users and supporters for putting up with the limitations of our software and working with us to improve it.

My thanks to my computer science co-advisor Leo Guibas for letting me spend all my time working on problems in biology and chemistry.

Finally, my heartfelt thanks to Vijay Pande for letting me spend years exploring the applications of deep learning to chemistry, biology, physics and more. Senior scientists who create a safe space for beginners to explore novel ideas are invaluable, and Vijay was brilliant in letting us explore crazy ideas while providing constant support.


}
\clearpage  % End of the Acknowledgements
%% ----------------------------------------------------------------

\pagestyle{fancy}  %The page style headers have been "empty" all this time, now use the "fancy" headers as defined before to bring them back


%% ----------------------------------------------------------------
\lhead{\emph{Contents}}  % Set the left side page header to "Contents"
\tableofcontents  % Write out the Table of Contents

%% ----------------------------------------------------------------
\lhead{\emph{List of Figures}}  % Set the left side page header to "List if Figures"
\listoffigures  % Write out the List of Figures

%% ----------------------------------------------------------------
\lhead{\emph{Molecular Machine Learning with DeepChem}}  % Set the left side page header to "List of Tables"
\listoftables  % Write out the List of Tables

%% ----------------------------------------------------------------
--
% End of the pre-able, contents and lists of things
% Begin the Dedication page

\setstretch{1.3}  % Return the line spacing back to 1.3

\pagestyle{empty}  % Page style needs to be empty for this page
\dedicatory{Dedicated to my family for their unstinting love, encouragement, and support}

\addtocontents{toc}{\vspace{2em}}  % Add a gap in the Contents, for aesthetics


%% ----------------------------------------------------------------
\mainmatter	  % Begin normal, numeric (1,2,3...) page numbering
\pagestyle{fancy}  % Return the page headers back to the "fancy" style

% Include the chapters of the thesis, as separate files
% Just uncomment the lines as you write the chapters
\clearpage
\input{Chapters/massively_multitask.tex}
%\clearpage
%\input{Chapters/moleculenet.tex}
\clearpage
\input{Chapters/low_data_drug_discovery.tex}
\clearpage
\input{Chapters/acnn.tex}
\clearpage
\input{Chapters/retrosynthesis.tex}
\clearpage
\input{Chapters/is_multitask_practical.tex}
\clearpage
\input{Chapters/bace.tex}



%% ----------------------------------------------------------------
% Now begin the Appendices, including them as separate files

\addtocontents{toc}{\vspace{2em}} % Add a gap in the Contents, for aesthetics

\appendix % Cue to tell LaTeX that the following 'chapters' are Appendices
\clearpage
\input{Appendices/appendix_massively_multitask.tex}
%\clearpage
%\input{Appendices/moleculenet_appendix.tex}
\clearpage
\input{Appendices/low_data_appendix.tex}
\clearpage
\input{Appendices/acnn_appendix.tex}
\clearpage
\input{Appendices/multitask_practical_appendix.tex}


\addtocontents{toc}{\vspace{2em}}  % Add a gap in the Contents, for aesthetics
\backmatter

%% ----------------------------------------------------------------
\label{Bibliography}
\lhead{\emph{Bibliography}}  % Change the left side page header to "Bibliography"
\bibliographystyle{unsrtnat}  % Use the "unsrtnat" BibTeX style for formatting the Bibliography
\bibliography{Bibliography}  % The references (bibliography) information are stored in the file named "Bibliography.bib"

\end{document}  % The End
%% ----------------------------------------------------------------